Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-04-25 paper.tex
Improved description of Figure 2

Figure~\ref{fig:iterations} illustrates this iterative process on the previous
exemplar pipeline.

\todo{Explain how graphs are represented.}

>>>>

\begin{figure}
  \includegraphics[scale=0.3]{images/iterative_modif}
  \caption{iteration of proposed modification.}
  \label{fig:iterations}
\end{figure}

Figure~\ref{fig:iterations} illustrates our iterative classification 
process for the example in Figure~\ref{fig:graph-example}. At every 
step, processes that created errors are shown in red, processes that 
removed errors are in blue, processes that propagated errors are in 
yellow, and other processes (transparent processes) are in green. As in 
Figure~\ref{fig:graph-example}, plain black edges represent the process 
tree and dashed edges represent file dependencies: green edges 
represent files with no errors, while red edges represent files with 
errors. Temporary files are not represented because they have been 
backed up as previously described.

The three steps in Figure~\ref{fig:iterations} correspond to the 
iterations of the classification algorithm At step one \texttt{2\#bet2} 
is classified as error creator (red) as it produced files with errors 
from files without error. \texttt{3\#fslstats} is classified as error 
remover (blue) as it produced files without errors from files with 
errors. \texttt{4\#fslmaths} and \texttt{5\#fslstats} are classified as 
unknown (yellow) as they produce files with errors from files with errors.

At step 2, the files produced by \texttt{2\#bet2} in the tested 
condition are replaced with the files produced by \texttt{2\#bet2} in 
the other condition. \texttt{3\#fslstats} is now classified as transparent, \texttt{4\#fslmaths} is now classified
as error creator and \texttt{5\#fslstats} is still unknown.

 At step 3, the files produced by \texttt{4\#fslmaths} in the tested 
 condition are replaced with the files produced by \texttt{4\#fslmaths} 
 in the other condition. \texttt{5\#fslstats} is now transparent.

 As a result of those 3 steps, the final process classification is: 
 \texttt{2\#bet2} and \texttt{4\#fslmath} are error creators (red), 
 \texttt{3\#fslstats} is error remover (blue) and the other processes 
 are transparent.

The process graphs of real pipelines are much larger than the one in 
Figure~\ref{fig:iterations}. To represent such large graphs, we 
summarize them by (1) building subgraphs for every interesting node 
(e.g. red and blue nodes with their children) (2) remove the 
interesting nodes from graph (3) finding largest connected components 
in the remaining nodes (iteratively).
